Programming Language Foundations in Agda

### 2019-07-15 papers/scp/PLFA.tex
fixed some wording

Philip considered himself fortunate that his student, Wen, was
keen to help.  She guided Philip as a newbie to Agda and provided an
infrastructure for the book that we found easy to use and produces
pages that are a pleasure to view.  The bulk of the first draft of the
book was written January--June 2018, while Philip was on sabbatical in
Rio de Janeiro.  After the first draft was published, Jeremy wrote
two further parts.  One explains a new and simple approach
to denotational semantics, developed as part of his research.  The
other develops important precursors to the semantics, including
confluence and big-step semantics.

@@

The book is broken into three parts. The first part, Logical Foundations,
develops the needed formalisms.  The second part, Programming Language
Foundations, introduces basic methods of operational semantics.
The third part, Denotational Semantics, introduces a simple
model of semantics, and shows it is compositional, sound, adequate, 
and implies contextual equivalence.
(SF is divided into books, the first two of which have the same names
as the first two parts of PLFA, and cover similar material.)

>>>>

Philip considered himself fortunate that his student, Wen, was
keen to help.  She guided Philip as a newbie to Agda and provided an
infrastructure for the book that we found easy to use and produces
pages that are a pleasure to view.  The bulk of the first draft of the
book was written January--June 2018, while Philip was on sabbatical in
Rio de Janeiro.  After the first draft was published, Jeremy wrote
eight additional chapters, covering aspects of operational and
denotational semantics.

@@

The book is broken into three parts. The first part, Logical Foundations,
develops the needed formalisms.  The second part, Programming Language
Foundations, introduces basic methods of operational semantics.
The third part, Denotational Semantics, introduces a simple
model of semantics and its properties.
(SF is divided into books, the first two of which have the same names
as the first two parts of PLFA, and cover similar material.)
Part~I and Part~II up to Untyped were written by Phil,
Part~II from Substitution and Part~III were written by Jeremy.
